Bayesian integration of networks without gold standards

### 2011-08-20 src/main/latex/paper/paper.tex
added description of beta priors

To determine the prior distribution $\pi(\theta)$, we have to consider the nature of the error rates $\alpha_i$ and $\beta_i$ as ``success rates'' for misreading each potential edge. Modelling each observation event over a potential edge as a Bernoulli experiment with such a success rate, the number of false positives and false negatives in an experimental graph $X_i$ would follow a binomial distribution. The success rates for a binomial distribution can be sampled using the Beta distribution. The Beta distribution is dependent on two parameters, $a$ and $b$.

However, instead of sampling from $\pi(\theta,G|X)$ directly, we employ Gibbs sampling \citep{gelfand_sampling-based_1990} and alternately sample from $\pi(\theta|G,X)$ and $\pi(G|\theta,X)$.

@@

The second step in each cycle is the sampling of a new error rate vector $\theta$ based on $G$. 
%FIXME
The parameters $a$ and $b$ can be interpreted as one plus the number of successes and failures, respectively, in a binomial distributed dataset. In order to obtain values for $a$ and $b$, one can compare each $X_i$ to the currently assumed true graph $G$ and use it to count the number of supposed True Positives (tp), False Positives (fp), True Negatives (tn) and False Negatives (fn). Then, the full conditionals for $\alpha$ and $\beta$ can be sampled as follows:
\begin{align}
  \alpha_i &\sim Be(\text{fp}_i+1, \text{tn}_i+1)\\
  \beta_i &\sim Be(\text{fn}_i+1, \text{tp}_i+1)
\end{align}.

>>>>

To determine the prior distribution $\pi(\theta)$, we have to consider the nature of the error rates $\alpha_i$ and $\beta_i$ as ``success rates'' for misreading each potential edge. Modelling each observation event over a potential edge as a Bernoulli experiment with such a success rate, the number of false positives and false negatives in an experimental graph $X_i$ would follow a binomial distribution. The success rates for a binomial distribution can be sampled using the Beta distribution. The Beta distribution is dependent on two parameters, $a$ and $b$. For the prior distribution we assume $a = b = 1$.

\begin{align}
  \alpha_i &\sim Be(a_\alpha, b_\alpha) \; \forall i=1,\ldots,n\\
  \beta_i &\sim Be(a_\beta, b_\beta) \; \forall i=1,\ldots,n
\end{align}.

Since sampling from $\pi(\theta,G|X)$ directly would be very difficult, we instead employ a Gibbs sampling approach \citep{gelfand_sampling-based_1990} and alternately sample from $\pi(\theta|G,X)$ and $\pi(G|\theta,X)$.

@@

The second step in each cycle is the sampling of a new error rate vector $\theta$ based on $G$. 
As explained above, Beta distributions can be used to describe the behaviour of $\theta$.
The parameters $a$ and $b$ can be interpreted as one plus the number of successes and failures, respectively, in a binomial distributed dataset. In order to obtain values for $a$ and $b$, one can compare each $X_i$ to the currently assumed true graph $G$ and use it to count the number of supposed True Positives (tp), False Positives (fp), True Negatives (tn) and False Negatives (fn). Then, the full conditionals for $\alpha$ and $\beta$ can be sampled as follows:
\begin{align}
  \alpha_i &\sim Be(\text{fp}_i+1, \text{tn}_i+1)\\
  \beta_i &\sim Be(\text{fn}_i+1, \text{tp}_i+1)
\end{align}.
